Finite Time Bounds for Temporal Difference Learning with Function Approximation: Bugs in state-of-the-art results

### 2017-07-30 issues.tex
pass on issues

\maketitle
\begin{abstract}
In mathematics, results build on previous results. Thus, it is important to keep the literature free of erroneous claims.
This short report lists some problems with the proofs and claims in the recent papers by \cite{flstd,lstdicml}, whose longer version containing the proofs are available on arxiv \citep{flstda,lstdicmla}. 
In particular, it follows that the results in these papers, if true, would need completely new proofs, and thus should not be used as stated by the authors.
\end{abstract}
\section{Introduction}
This short report lists some problems with the proofs of the claims in two recent papers  by \cite{flstd,lstdicml}.
As the problems seem serious, our conclusion is that to obtain results similar to those claimed in these two works, the assumptions of the stated claims need to be considerably strengthened and the form of the results will also need to be adjusted in significant ways.

>>>>

\maketitle
\begin{abstract}
In all branches of mathematics, including learning theory,
results build on previous results. Thus, it is important to keep the literature free of erroneous claims.
This short report lists some problems with the proofs and claims in the recent papers by \cite{flstd,lstdicml}, whose longer version containing the proofs are available on arxiv \citep{flstda,lstdicmla}. 
In particular, it follows that the results in these papers, if true, would need completely new proofs, and thus should not be used in the form stated by the authors.
\end{abstract}
\section{Introduction}
This short report lists some problems with the proofs of the claims in two recent papers  by \cite{flstd,lstdicml}.
As the problems seem serious, our conclusion is that to obtain results similar to those claimed in these two works, the assumptions of the stated claims need to be considerably strengthened and the form of the results will also need to be adjusted in significant ways.
